Waving and swaying

### 2014-01-25 Paper/grass.tex

% shows 
%this critical number for different grass density and grass height along with experimental threshold observed by Grizzle (1996)
\begin{figure}[htb!]
\includegraphics[scale=0.8]{Critical_Re_vs_Ng_Grizzle}
\caption{Critical Reynolds number with flow between parallel plate for different grass height as a function of grass number density}
\end{figure}
\begin{figure}[htb!]
\includegraphics[]{K_vs_shear_width}
\caption{Critical Wavenumber with for different grass height as a function of shear layer thickness}
\end{figure}
\begin{figure}[htb!]
\includegraphics[scale=0.34]{Observed_vs_calculated}
\caption{Comparison between experimently oberved frequency and predicted frequency from model}
\end{figure}

>>>>

% shows 
%this critical number for different grass density and grass height along with experimental threshold observed by Grizzle (1996)
\begin{figure}[htb!]
\includegraphics[scale=0.8]{Critical_Re_vs_Ng_Grizzle}
\caption{Critical Reynolds number with flow between parallel plate for different grass height as a function of grass number density}
\end{figure}
\begin{figure}[htb!]
\includegraphics[]{K_vs_shear_width}
\caption{Critical Wavenumber for different grass height as function of shear layer thickness}
\end{figure}
\begin{figure}[htb!]
\includegraphics[scale=0.34]{Observed_vs_calculated}
\caption{Comparison between experimently oberved frequency and predicted frequency}
\end{figure}
